\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\begin{document}

To\\
The Editor-in-Chief\\
JMIR Medical Informatics

\bigskip

Subject: Submission of manuscript ``FirstContact: A Human-in-the-Loop and Trustworthy AI Triage System for Integrated Teleconsultation and Insurance Guidance''

\bigskip

Dear Editor,

\bigskip

I would like to submit the manuscript entitled ``FirstContact: A Human-in-the-Loop and Trustworthy AI Triage System for Integrated Teleconsultation and Insurance Guidance'' for consideration as an Original Paper in JMIR Medical Informatics.

This work presents FirstContact, a human-in-the-loop clinical decision support system for digital triage that integrates an ensemble machine learning triage engine, teleconsultation and doctor discovery modules, and a patient-facing insurance guidance workflow.

From a medical informatics and clinical decision support perspective, the main contributions are:

1. A modular architecture that embeds AI-driven triage within a full digital care pathway, spanning web front end, Node.js/Express back end, Python-based machine learning engine, and MongoDB data layer.

2. A Random Forest-based triage model for mixed demographic, vital, laboratory, symptom, and lifestyle data, evaluated with detailed performance metrics, confidence intervals, and baseline comparisons.

3. A trustworthy clinical decision support framework combining explainability based on feature attribution, probability calibration including Brier score and reliability diagram, cost-sensitive triage threshold analysis with sensitivity, specificity, and positive predictive value tradeoffs, and fairness evaluation across demographic subgroups.

4. A human-in-the-loop workflow in which clinicians remain final decision-makers, can override AI suggestions, and can use model explanations and subgroup performance summaries for oversight and future model refinement.

We believe this manuscript is a good fit for JMIR Medical Informatics because it lies at the intersection of clinical decision support, artificial intelligence in healthcare, and digital health infrastructures, and it explicitly addresses explainability, calibration, fairness, and human oversight, which are central to trustworthy clinical AI.

The manuscript is not under consideration for publication elsewhere, and it has not been published previously in any language or format. I confirm that I am the sole author and that I have approved the final version of the manuscript and agree with its submission to your journal.

There are no conflicts of interest to declare. If applicable, details regarding data sources, ethics, and funding are provided in the manuscript.

Thank you for considering this submission. I would be grateful for the opportunity to have the manuscript reviewed for publication in JMIR Medical Informatics.

\bigskip

Sincerely,

\bigskip

YOUR FULL NAME\\
Department of Computer Science, YOUR INSTITUTION\\
Email: YOUR EMAIL

\end{document}

