\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\begin{document}

\section*{Declarations}

\subsection*{Conflicts of Interest}

The author declares no conflicts of interest.

\subsection*{Funding}

This research did not receive any specific grant from funding agencies in the public, commercial, or not-for-profit sectors.

\subsection*{Ethics Approval and Consent to Participate}

This study primarily relied on a synthetic dataset constructed from ranges and co-occurrence patterns reported in the clinical literature and on a publicly available cardiovascular risk dataset. No identifiable patient data were used. For the synthetic data and public dataset components, formal institutional review board approval was not required according to local regulations. If the system is later evaluated on de-identified clinical data, appropriate ethics approvals and governance processes will be obtained.

\subsection*{Consent for Publication}

Not applicable.

\subsection*{Availability of Data and Materials}

The synthetic dataset generation procedure and analysis code used in this study can be made available from the author upon reasonable request. The external cardiovascular dataset used for validation is publicly available from its original source, as cited in the manuscript.

\subsection*{Author Contributions}

The author conceived the study, designed the architecture, implemented the system, performed the experiments, analysed the results, and wrote the manuscript.

\end{document}

